Xor & Some Final analysis

### 2021-09-14 analysis/xor-some_final.Rmd
test conjunction of H by trigger

>>>>

```{r}
# tiny update for separating the trigger words 
test_conjunction_of_all_hypotheses2 <-  function(posterior_hypotheses, trigger) {
  posterior_hypotheses %>% 
    mutate(hypothesis_true = case_when(
      key == paste('competence_', trigger, sep='') ~ positive_eff > 0.95,
      key == paste('prior_', trigger, sep='') ~ negative_eff > 0.95,
      key == paste('relevance_', trigger, sep='') ~ positive_eff > 0.95
    )) %>% 
    pull(hypothesis_true) %>% all()
}
# applied to the pilot data
test_conjunction_of_all_hypotheses2(posterior_hypotheses, "xor")
test_conjunction_of_all_hypotheses2(posterior_hypotheses, "some")
```
